### 2018-04-28 paper/security-analysis.tex

\dots

The message \(m\) remains the same from hop to hop during the onion routing, 
hence a global observer can track the message through the network.

We can choose different properties for \(\Enc*\).
What makes sense is to choose an authenticated encryption 
scheme~\cite{AuthEncryption}.
We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, \eg 
the one by \textcite{OTPKX} which is both deniable and authenticated and 
provides \ac{DEN-SS}.

>>>>

\commentDaniel{Under editing.}

The message \(m\) remains the same from hop to hop during the onion routing, 
hence a global observer can track the message through the network.
The same applies if one node occurs more than once in a route, \eg in both 
Alice's and Bob's part of the route.

Since we have an in-package header, each node on the route can infer its 
position on the route.
\commentDaniel{Maybe this can be solved by issue \#33.}

We can choose different properties for \(\Enc*\).
What makes sense is to choose at least an authenticated encryption 
scheme~\cite{AuthEncryption}.
We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, \eg 
the one by \textcite{OTPKX} which is both deniable and authenticated and 
provides \ac{DEN-SS}.
